NEED TITLE

### 2015-05-28 ms.tex
minor changes to the ms.tex and included a new file for the whole simulation named movieframe_quad2_0498.png

Here we will focus on the physics of rapid star formation and accretion.  An early model of Shu (1977) estimated the accretion rate onto stars by 
assuming that stars form from hydrostatic cores
supported by thermal gas pressure. The accretion
rate in his model was independent of time, given
by $M = m0c_s^3/G$, where $c_s$  is the
sound speed in molecular gas, and $m_0 = 0.975$.
Shu (1977) predicted a maximum accretion rate was $yr^{-1}$, which is too small to explain
the origin of massive stars.

@@

Recently Murray \& Chang (2015) developed a 1-D model of spherical collapse that treat turbulence as a dynamical variable and does not assume that the initial condition is a hydrostatically supported region.  They were able to accomplished this by taking advantage of the recent results of Robertson \& Goldreich (2012) on compressible turbulence.   In particular

@@

We use the adaptive mesh refinement code FLASH ver. 4.0.1 (Fryxell et al.
2000
; Dubey
et al.
2008
) to model isothermal, self-gravitating, hydrodynamic turbulence on isothermal gas with three-dimensional (3D),
periodic grids and 10 levels of refinement on a root grid of $128^3$, giving an effective resolution of $128K^3$.  
Self-gravity is computed with a multi-grid Poisson solver (see Ricker
2008), coupled with a fast-Fourier transform solution on the root grid.

To initialize our simulations, we drive turbulence by applying a large scale ($1 \le k \le 2$) solenoidal 
acceleration field as a momentum and energy source term.  We apply this field in the absence of gravity and sink particle formation for 3 dynamical times until a statistical steady state is reached.
{\bf WHY JUST SOLENOIDAL}

@@

We have also implemented a new algorithm for mesh refinement in these simulations.  As gas collapse under self gravity, certain regions rapidly increase in density.  These regions are refine when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
refinement criteria
\end{equation}
which when met causes the local grid to be refined by a factor of 2 provided that the maximum refinement level is not reached.

When the Truelove criterion is met at highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell.  This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution.  We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.

@@

To initialize our simulation, we begin by applying solenoidal stirring forces to the uniform, periodic simulation volume at the root grid resolution of $128^3$ until statistical equilibrium is reached (approximately three crossing times).  After this equilibrium is established, we then apply self gravity, adaptive mesh refinement, and sink particle creation.  In Figure \ref{fig:entire projection} we show a projection along the x-axis of the entire simulation volume that has up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. Regions that are highly refined are the densest regions which are smoother than the low-density more pixelated regions.
\begin{figure}
\plotone{frame0241.png}
\caption{Projection along the x-axis of the entire simulation volume. The root grid is $128^3$ with up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. This snapshot is taken at ??. \label{fig:entire projection}}
\end{figure}

>>>>

Here we will focus on the physics of rapid star formation and accretion.  An early model of Shu (1977) estimated the accretion rate onto stars by 
assuming that stars form from hydrostatic cores
supported by thermal gas pressure. The accretion
rate in his model was independent of time, given
by $M = m_0c_s^3/G$, where $c_s$  is the
sound speed in molecular gas, and $m_0 = 0.975$.
Shu (1977) predicted a maximum accretion rate was $yr^{-1}$, which is too small to explain
the origin of massive stars.

@@

Recently Murray \& Chang (2015), hereafter MC15, developed a 1-D model of spherical collapse that treat turbulence as a dynamical variable and does not assume that the initial condition is a hydrostatically supported region.  They were able to accomplished this by taking advantage of the recent results of Robertson \& Goldreich (2012) on compressible turbulence.   In particular

@@

We use the adaptive mesh refinement code FLASH ver. 4.0.1 (Fryxell et al.
2000
; Dubey
et al.
2008
) to model isothermal, self-gravitating, hydrodynamic turbulence on isothermal gas with three-dimensional (3D),
periodic grids and 8 levels of refinement on a root grid of $128^3$, giving an effective resolution of $32K^3$.  
Self-gravity is computed with a multi-grid Poisson solver (see Ricker
2008), coupled with a fast-Fourier transform solution on the root grid. Similar to (Lee et. al Feb. 2015) our FLASH runs use the Harten-Lax-van Leer-Contact Riemann solver and an unsplit solver. ({\bf Lee et. al use Lee \& Deane (2009) do we?})

We start with a box with the physical length set to $L = 16$pc using periodic boundary condtions. The intial mass density is $\rho = 3x10^{-22}$ and the isothermal, ambient gas is set to a sound speed of $c_s = 2.64x10^{4}$ {\bf we also set $Mach_ambient = 5.0$ include?}. To initialize our simulations, we drive turbulence by applying a large scale ($1 \le kL \le 2$) solenoidal acceleration field as a momentum and energy source term. We apply this field in the absence of gravity and sink particle formation for 3 dynamical times until a statistical steady state is reached.
{\bf WHY JUST SOLENOIDAL}

@@

We have also implemented a new algorithm for mesh refinement in these simulations. As gas collapse under self gravity, certain regions rapidly increase in density. These regions are refined when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
%\frac{\rho}{\rho_0} = 45 \text{x} 4^{l} (\frac{N_{root}}{128})^2 (\frac{16\text{pc}}{L})^2 (\frac{c_s}{2.65x10^4 \text{cm s})^2 (\frac{3x10^{-22}\text{g cm^-3}}{\rho_0})
\label{eq:refinement_criteria}
\end{equation}
which when met causes the local grid to be refined by a factor of 2 provided that the maximum refinement level is not reached.

When the Truelove criterion is met at highest refinement level, the excess mass in a cell is transferred either to a newly created sink particle or to a sink particle whose accretion radius includes the cell.  This behavior is the same as in Lee et al. (2014), albeit at a much higher resolution.  We should also note that like Lee et al. (2014), our sink particle creation prescription is different from the prescription of Federrath et al (???) where additional checks need to be performed.
Our base grid's resolution of $128^3$ gives a cell length of $1.2 \text{x} 10^{-1}$pc which is sufficient to resolve the Jean's length
\begin{equation}
\lambda_J \equiv \sqrt{\frac{\pi c_{s}^2}{G \bar{\rho}}} \approx 3.5 \text{pc}
\end{equation}

@@

To initialize our simulation, we begin by applying solenoidal stirring forces to the uniform, periodic simulation volume at the root grid resolution of $128^3$ until statistical equilibrium is reached (approximately three crossing times).  After this equilibrium is established, we then apply self gravity, adaptive mesh refinement, and sink particle creation.  In Figure \ref{fig:entire projection} we show a projection along the x-axis of the entire simulation volume that has up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. Regions that are highly refined are the densest regions which are smoother than the low-density more pixelated regions.
\begin{figure}
\plotone{movieframe_quad2_0498.png}
\caption{Projection of the density along the z-axis of the entire simulation volume. The root grid is $128^3$ with up to 8 levels of refinement, giving an effective resolution of $32\,{\rm K}^3$. This snapshot is taken $2.8$Myr after star formation is turned on. \label{fig:entire projection}}
\end{figure}
